Bird beak's elaboration and innovation

### 2023-05-11 Analysis/07-Orthogonality_and_statistics.Rmd
Update 07-Orthogonality_and_statistics.Rmd

elab <- 
  ggplot(fake, aes(x = elaboration, colour=Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("goldenrod", "#1E65A7")) +
  xlab("Relative elaboration") +
  ylab("Density") +
  theme(legend.position = "none") +
  labs(tags="a")

innov <-
  ggplot(fake, aes(x = innovation, colour = Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("goldenrod", "#1E65A7")) +
  xlab("Relative innovation") + 
  theme(legend.position = c(0.8, 0.8)) +
  labs(tags="b")

>>>>

elab <- 
  ggplot(fake, aes(x = elaboration, colour=Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("yellow", "purple")) +
  xlab("Relative elaboration") +
  ylab("Density") +
  theme(legend.position = "none") +
  labs(tags="a")

innov <-
  ggplot(fake, aes(x = innovation, colour = Level, fill = Level, ..scaled..)) +
  geom_density(alpha = 0.5) +
  theme_classic(base_size = 14) +
  scale_colour_manual(values = c(rgb(0,0,0,0), rgb(0,0,0,0))) +
  scale_fill_manual(values = c("yellow", "purple")) +
  xlab("Relative innovation") + 
  theme(legend.position = c(0.8, 0.8)) +
  labs(tags="b")
